Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-01-07 manuscript/climate_sensitivity_draft.Rmd
removed "interactively" shape from abstract

### Summary
- As climate change is driving increased drought in many forested regions around the world, mechanistic understanding of factors conferring drought resistance in trees is increasingly important. The dendrochronological record provides a window through which we can understand how tree size and species’ traits interactively shape tree growth responses during droughts.

- We analyzed tree-ring records for twelve species of an oak-hickory forest - representing 97% of woody productivity - in the 25.6-ha ForestGEO plot in Virginia (USA) to determine how tree size, microenvironment characteristics, and species' traits interactively shape drought responses across the three strongest regional droughts over a 60-year period (1950 - 2009).

>>>>

### Summary
- As climate change is driving increased drought in many forested regions around the world, mechanistic understanding of factors conferring drought resistance in trees is increasingly important. The dendrochronological record provides a window through which we can understand how tree size and species’ traits shape tree growth responses during droughts.

- We analyzed tree-ring records for twelve species of an oak-hickory forest - representing 97% of woody productivity - in the 25.6-ha ForestGEO plot in Virginia (USA) to determine how tree size, microenvironment characteristics, and species' traits shaped drought responses across the three strongest regional droughts over a 60-year period (1950 - 2009).
